Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-21 sections/eval.tex
Update on Overleaf.

>>>>

\begin{table}[htbp]
    \centering
    \caption{SpMV Tensor Formats}
    \begin{tabular}{|l|l|l|}
        \hline
        \textbf{Tensor Format} & \textbf{Style of Matrix} & \textbf{Evaluation Datasets} \\
        \hline
        SparseList & sparse matrices & Vuduc, Ahrens, TACO, SNAP, synthetic \\
        \hline
        SparseVBL & matrices with a clear blocked structure & Vuduc, Ahrens, TACO, SNAP, synthetic  \\
        \hline 
        SparseBand & matrices with a diagonal band & Vuduc, Ahrens, TACO, SNAP, synthetic \\ 
        \hline 
        SparsePoint & matrices with one value per row & synthetic \\
        \hline
        Element* & matrices with real values & Vuduc, Ahrens, TACO, synthetic \\
        \hline
        Pattern* & matrices with boolean values & SNAP  \\
        \hline 
    \end{tabular}
    \footnotesize *Used in conjunction with aforementioned formats as the innermost level to represent scalar values.
\end{table}

\begin{table}[htbp]
    \centering
    \caption{SpMV Tensor Formats}
    \begin{tabular}{|l|l|l|l|l|}
        \hline
        \textbf{Tensor Format} & \textbf{Style of Matrix} & \textbf{Evaluation Datasets} \\
        \hline
        SparseList & sparse matrices & Vuduc, Ahrens, TACO, SNAP, synthetic \\
        \hline
        SparseVBL & matrices with a clear blocked structure & Vuduc, Ahrens, TACO, SNAP, synthetic  \\
        \hline 
        SparseBand & matrices with a diagonal band & Vuduc, Ahrens, TACO, SNAP, synthetic \\ 
        \hline 
        SparsePoint & matrices with one value per row & synthetic \\
        \hline
        Element* & matrices with real values & Vuduc, Ahrens, TACO, synthetic \\
        \hline
        Pattern* & matrices with boolean values & SNAP  \\
        \hline 
    \end{tabular}
    \footnotesize *Used in conjunction with aforementioned formats as the innermost level to represent scalar values.
\end{table}
